---
title: "ggplot 1"
author: "Xueqing Huang"
date: "2021/10/5"
output: github_document
---

```{r}
library(tidyverse)
library(ggridges)
```

Load in a dataset that we'll use often.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## Scatterplots!!

Create my first scatterpolot ever.


```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) 

weather_plot + geom_point()
  
```

## Advanced sactterplot

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() +
  geom_smooth(se = FALSE)
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name)) +
  geom_smooth(se = FALSE)
```

Let's facet some things.

```{r}
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, alpha = tmin, color = name)) +
  geom_point(alpha = .2, size = 2) + 
  geom_smooth(se = FALSE, size = 2) +
  facet_grid(. ~ name)

```

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, size = prcp)) + 
  geom_point(alpha = .3 ) +
  facet_grid(. ~ name) +
  geom_smooth(se = FALSE)

```

Let's combine some elements and try a new plot.

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) + 
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

## Some small notes.

How many geoms have to exist?

You can have whatever geoms you want.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```

You can use a net geom!

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_density2d() +
  geom_point(alpha = .3)
```

## Univariate plot

Histograms.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) +
  geom_histogram()
```

add color.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram(position = "dodge")
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) +
  geom_histogram() +
  facet_grid(. ~ name)
```

a new geometry.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = .3)
```

boxplot.

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmax)) + 
  geom_boxplot()
```

trendy plots

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) + 
  geom_violin() +
  stat_summary(full = "median")
  
```

ridge plot.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) + 
  geom_density_ridges()
```

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  mutate(
    tmax = tmax * (9/5) + 32,
    tmin = tmin * (9/5) + 32
  ) %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Save a scatterplot.

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5)

ggsave("weather_plot.pdf", weather_plot, width = 8, height = 5)
```

embedding.

```{r fig.width=6, fig.height=3}
weather_plot
```

```{r fig.width=12, fig.height=6}
weather_plot

```



